%-------------------------
% Resume in Latex
% Author : Urvashi
% Based on: https://github.com/jakegut/resume (which was based on https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \vspace{-4pt}
  \color{gray}
  \item
\end{flushright}

\vspace{-7pt}

\begin{center}
    \textbf{\Huge \scshape URVASHI BHARGAVA} \\ \vspace{8pt}
    \small 
    \faIcon{phone}
    \href{tel:+919550064000}{+919550064000}
    \faIcon{code}
    \href{https://urvashiportfolio.com/}
    {\underline{urvashiportfolio.com}} $  $
    \faIcon{github}
    \href{https://github.com/urvashii-b}
    {\underline{urvashii-b}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/urvashi-bhargava-b66100262/}{\underline{urvashi}} $  $
    \faIcon{trophy}
    \href{https://leetcode.com/urvashiiibh/}{\underline{urvashiiibh}} $  $
    \faIcon{envelope}
    \href{mailto:urvashi.officialcse@gmail.com}
    {\underline{urvashi.officialcse@gmail.com}} $  $
    
    
\end{center}

    
% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {PES University - Bengaluru, India}{December 2021 - 2025}
      {Bachelor of Technology: Computer Science}{Current CGPA: 8.78/10}

    \resumeSubheading
      {Delhi Public School - Hyderabad, India}{August 2016 - May 2019}
      {High School}{X (CBSE): 96.4}
      
    \vspace{3pt}
  \resumeSubHeadingListEnd
    
% -------------------- SKILLS --------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{

     \textbf{Languages}{: Python, C++, R, HTML/CSS} \\
     

     \textbf{Databases}{: MySQL, MongoDB, Neo4j} \\
     
     \textbf{Libraries}{: Keras, TensorFlow, NumPy, scikit-learn}  \\

     \textbf{Strengths}{: Database Management System, Data Analytics, Machine Intelligence, Graph theory} \\
    }}
 \end{itemize}

% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{Royal Resolve - N Queens Game} $|$ 
        \href{https://github.com/urvashii-b/RoyalResolve-NQueens}{\color{blue}\faIcon{github}}}{Aug 2022 - Dec 2022}
        \resumeItemListStart
            \resumeItem{Designed and implemented Royal Resolve, a Python-based project that not only addresses the N-Queens problem with a solution but also serves as an interactive game allowing users to input the board size.}
            \resumeItem{Proficiently implemented the backtracking solution and created an interactive GUI using Tkinter.}   
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{Student Database Management System - StudentHub} $|$ \href{https://github.com/urvashii-b/StudentHub}{\color{blue}\faIcon{github}} }{September 2023 -- Nov 2023}
        \resumeItemListStart
            \resumeItem{Developed StudentHub using Flask and MySQL to proficiently organize and manage diverse student data.}
            \resumeItem{Incorporated user authentication alongside advanced search and filter capabilities, ensuring consistency and efficient retrieval of student information.}
            \resumeItem{Created a user-friendly website interface, serving as a reliable solution for educational institutions.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{AR/AI Fashion Store - ArBotique} $|$ {Kodikon 3.0} $|$ {Collaborative project} $|$ \href{https://github.com/urvashii-b/11_ArBotique}{\color{blue}\faIcon{github}}}
        {4-5 November 2023}
        \resumeItemListStart
            \resumeItem{Implemented AR technology for seamless virtual try-ons, enabling customers to visualize apparel before purchase, resulting in a more informed shopping experience.}
            \resumeItem{Innovatively integrated DALL-E by OpenAI, utilizing TNN model for personalized clothing customization.}
            \resumeItem{Designed 3D Models using Blender for accessories display.}
        \resumeItemListEnd

        \begin{comment}
        /*\resumeProjectHeading
        {\textbf{Student Portal - CodeCampus} $|$ \href{https://github.com/urvashii-b/decode}{\faIcon{github}}}{6th September 2023 - Present}
        \resumeItemListStart
            \resumeItem{Executed the 'CodeCampus' project, revolutionizing the digital learning experience for our university.}
            \resumeItem{The platform streamlined assignment submission and grading processes, resulting in 20 \% improvement in student satisfaction.} 
            \resumeItem{Enhanced the project by introducing advanced features like plagiarism detection and role-based login providing security features.} 
        \resumeItemListEnd
        \end{comment}
    \resumeSubHeadingListEnd

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Joy Store India} $|$ \footnotesize\emph{Graphic Designer}\vspace{3pt}}{May 2023 - August 2023}
          \resumeItemListStart
            \resumeItem{Curated the visual identity of Joy Store India, spearheading logo designs, banners, and brand establishment.}
            \resumeItem{As the project leader, Upheld software engineering principles, ensuring timely completion and project closure.}
            \resumeItem{Directed marketing strategies, applying my skills to enhance outreach and amplify the presence of JSI as well.}
        \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{HackerSpace PESU ECC} $|$ \footnotesize\emph{Design Team Member}\vspace{8pt}}{March 2022 - June 2023}
          \href{https://www.instagram.com/p/CbHnbkPAqs2/?igshid=MzRlODBiNWFlZA%3D%3D&img_index=1}{\small{Collaborated within a dynamic design team, contributing creative insights for the success of numerous workshops.}}
       \resumeProjectHeading
          {\textbf{Synthax Hackathon} $|$ \footnotesize\emph{Mentor}}{27-28 January 2024}
            \resumeItemListStart
                \resumeItem{Gained valuable mentoring experience after being chosen as a mentor at the Harvest International School.}
            \resumeItemListEnd
   \resumeSubHeadingListEnd 

% -------------------- ACHIEVEMENTS --------------------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{MRD Scholarship: }\href{https://drive.google.com/file/d/165MKp1oXSgvJpZoC17rnhxoq5BZP28Va/view?usp=sharing}{\underline{\faTrophy{}  Top 20\%}{ of the students in the University}} \\
    

     \textbf{Top 10 in Kodikon 3.0: }{Led the team to an impressive }\href{https://drive.google.com/file/d/1zE2c2vQAUzSWOnhfeUJ2MOQWz7Egtn11/view?usp=sharing}{\underline{top-10}}{ finish at the national-level hackathon.} \\

     \textbf{Top 30 in Smart India Hackathon}{: Led the team to secure a prestigious position representing the university.} \\ 
    }}
 \end{itemize}
% -------------------- CERIFICATIONS --------------------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{

    \textbf{Database Structures and Management with MySQL:}{ \href{https://drive.google.com/file/d/1yk1cgDVw4zl7LSJ7ZCwm0mTG6D1OUiyl/view?usp=sharing}{\color{blue}\underline{Meta}} }\\

\textbf{Jira Work Management Fundamentals Badge:}{ \href{https://university.atlassian.com/student/award/YUXGUbPbH1wfKhPqoE3UvJ1E}{\color{blue}\underline{Atlassian}}} \\
    
     \textbf{A Beginner's Guide to Linux Kernel Development (LFD103):}{ \href{https://drive.google.com/file/d/1Rc3an_g4eF2UVKEvh6tCYHMYul08s1O3/view?usp=sharing}{\color{blue}\underline{The Linux Foundation}}} \\
     
     \textbf{Centre for Innovation and Entrepreneurship -  Level 1: }\href{https://drive.google.com/file/d/1TqpBAXJ2q6YzqMNAOdY6SA-zIz7lrH5G/view?usp=sharing}{\color{blue}\underline{PES University}} \\

    \textbf{Getting Started with Compute (Lab): }{\color{blue}\underline{AWS Educate}} \\

    }}
 \end{itemize}
\end{document}
